\section{Task 1}
Question 1
-	COVID and normal chest X-rays can have subtle visual differences, making it hard for a model to learn the differences between classes.
-	The dataset size is relatively small (only 1600 training images), which increases the risk of overfitting.
-	X-ray images often have variability in terms of brightness, contrast, and anatomical differences between individuals, which introduce noise
-	If the dataset is not perfectly balanced the model might become biased toward the majority class but fortunately, the plot shows that this is not the case here.
Question 2
Based on the pixel statistics and label distribution, the datasets appear to be fairly uniformly divided, though not perfectly. The average pixel values and standard deviations are similar across sets — training (mean ≈ 0.53, std ≈ 0.25), validation (mean ≈ 0.55, std ≈ 0.26), and test (mean ≈ 0.55, std ≈ 0.26) — indicating consistent image intensity. The class distribution also looks well balanced overall. The training set is evenly split, while the validation set shows a slight tilt toward NORMAL, and the test set has a few more COVID samples. These minor differences are not concerning. Overall, the datasets are reasonably well-balanced in terms of both pixel characteristics and label distribution.
Question 3
COVID-19 lesions often appear as ground-glass opacities or consolidation patches, which have different intensity distributions compared to normal lungs.
If these variations between the COVID-positive and normal X-rays are not addressed properly (e.g., by normalization or augmentation), the model could fail to learn the correct patterns, reducing its accuracy. This issue might cause the model to misinterpret lesions as part of normal anatomy or vice versa.Unaccounted-for artifacts can mislead the model by focusing on irrelevant patterns. It’s crucial to ensure that image pre-processing (such as normalization and augmentation) reduces the impact of these artifacts. This would help the model focus on medically relevant features rather than on noise or imaging imperfections.
